Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-13 paper/disc20clustering.tex
rewriting the LB (1)

\begin{proof}
	Fix any online algorithm \ALG.
	For a ground set $C$ of nodes that are initially collocated in one cluster,
	let $I(C)$ denote the cluster.
%	If $C$ contains nodes that originate from different clusters
%	then $I(C)$ is undefined.
	Throughout the construction, we maintain ground sets for each node.
	Initially, all nodes are isolated (i.e., in singleton ground sets).
	First, we choose a cluster arbitrarily and
	 create a~ground set $B$ of $k-1$ nodes in this cluster.
	%We never dismiss any constructed ground set.
	Each cluster hosts exactly $k$ nodes, and in any partition, a~single isolated node must be collocated with $B$.
	We say that this isolated node that accompanies the ground set $B$ is \emph{special}.
	We denote the first special node by $x_0$.

	Then, we join the special node to a~larger ground set to force its eviction.
	Precisely,
	we create a~ground set $\{x_0, y_0\}$, 
	where $x_0$ is the current special node and $y_0$ is an arbitrary isolated node.
	Since \ALG does not have $\{x_0,y_0\}$ collocated, 
	we issue an external request between them so that \ALG collocates them.
	\ALG cannot collocate $\{x_0, y_0\}$ with $B$ (as $B$'s size is $k-1$), hence it collocates them in a different cluster.
	In order to preserve a~feasible partition of nodes after collocating $\{x_0, y_0\}$,
	\ALG must replace $x_0$ with another isolated node.
%	denoted by $x_1$.

	We proceed by joining the current special node to a~larger ground set,
	as long as a feasible partition exists afterwards.
	Consider the isolated node $x_i$ currently collocated with $B$.
	 We issue a request between $x_i$ and some node $y_i \in C_i$,
	 where $C_i$ is the largest ground set
	 s.t.~$I(C_i) = I(x_i), C_i \neq \{x_0,y_0\}$,
	 only if  a feasible partition exists
	 that collocates all nodes in $\{x_i\} \cup C_i $.
	Any such feasible partition replaces $x_i$ with some isolated node $x_{i+1}$,
	as the new ground set $\{x_i\} \cup C_i $  may not be ever split.
	Otherwise,
	if no such feasible partition exists,
	 then we terminate the process and
	 we let $x^* := x_i, y^*:=y_i$.

>>>>

\begin{proof}
	Fix any online algorithm \ALG.
	For a ground set $C$ of nodes that are initially collocated in one cluster,
	let $I(C)$ denote the cluster.
%	If $C$ contains nodes that originate from different clusters
%	then $I(C)$ is undefined.
%	Throughout the construction, we maintain ground sets for each node.
	Initially, all nodes are isolated, i.e., each node is in a singleton ground set.
	First, we choose a cluster arbitrarily and
	 create a~ground set $B$ of $k-1$ nodes in this cluster.
	%We never dismiss any constructed ground set.
	Each cluster hosts exactly $k$ nodes, and in any feasible partition,
	 a~single isolated node must be collocated with $B$.
	At any time,
	we refer to the isolated node currently collocated with $B$ as the \emph{special} node.
	Let $x_0$ denote the first special node.

	Then, we join the special node to a~larger ground set to force its eviction.
	Precisely,
	we create a~ground set $\{x_0, y_0\}$, 	where
%	 $x_0$ is the current special node and
	 $y_0$ is an arbitrary isolated node.
	Since \ALG does not have $\{x_0,y_0\}$ collocated, 
	we issue an external request between them so that \ALG collocates them.
	\ALG cannot collocate $\{x_0, y_0\}$ with $B$ (as $B$'s size is $k-1$), hence it collocates them in a different cluster.
	In order to preserve a~feasible partition of nodes after collocating $\{x_0, y_0\}$,
	\ALG must replace $x_0$ with another isolated node.
%	denoted by $x_1$.

	We proceed by joining the current special node to a~larger ground set in a similar way,
	as long as a feasible partition exists afterwards.
	Consider the isolated node $x_i$ currently collocated with $B$.
	 We issue a request between $x_i$ and some node $y_i \in C_i$,
	 where $C_i$ is the largest ground set
	 s.t.~$I(C_i) = I(x_i), C_i \neq \{x_0,y_0\}$,
	 only if  a feasible partition exists
	 that collocates all nodes in $\{x_i\} \cup C_i $.
	Any such feasible partition replaces $x_i$ with some isolated node $x_{i+1}$,
	as the new ground set $\{x_i\} \cup C_i $  may not be ever split.
	Otherwise,
	no such feasible partition exists,
	we terminate the process and
	 we let $x^* := x_i, y^*:=y_i$.
